### 2016-03-14 HSF-TN/draft-2016-VACPLAT/draft-HSF-TN-2016-VACPLAT.tex
Improved wording

The term ``resource provider'' is used to refer to the entity which is 
able to take the decision about creating each VM. That is, the decision 
about whether resources will be provided or not. Typically, this is owner 
of an OpenStack or other cloud tenancy managed by Vcycle or the manager of Vac VM 
factories. Beyond this may be many layers of resource provision
in terms of legal owners of services and hardware and even funding agencies.

A location at which VMs can be created managed by one or more VMLMs
which are cooperating to achieve a set of target shares is referred to
as a ``space''. This is equivalent to a Compute Element at a Grid site,
and spaces must be given DNS names in DNS space available to the
resource provider. However, it is not necessary to register the 
space name in the corresponding DNS zone. For Vac, a space is a set
of VM factory machines which are communicating via VacQuery and may
be said to be neighbours. For Vcycle, a space corresponds to an 
OpenStack tenancy or project, with a specified endpoint to contact
and identity tokens to use.

>>>>

The term ``resource provider'' is used to refer to the entity which is 
able to take the decision about creating each VM. That is, the decision 
about whether resources will be provided or not. Typically, this is owner 
of an OpenStack or other cloud tenancy managed by Vcycle or the manager of Vac VM 
factories. The term is not used here to refer to higher or lower layers of resource
provision in terms of legal owners of services and hardware, funding
agencies, operators of the site infrastructure etc.

A location at which VMs can be created managed by one or more VMLMs
which are cooperating to achieve a set of target shares is referred to
as a ``space''. This is equivalent to a Compute Element (CE) at a Grid site,
and spaces must be given CE-style DNS names in DNS space available to the
resource provider. However, it is not necessary to register the 
space name in the corresponding DNS zone. For Vac, a space is a set
of VM factory machines which are communicating via VacQuery and may
be said to be neighbours. For Vcycle, a space corresponds to an 
OpenStack or similar tenancy or project, with a specified endpoint to 
contact and identity tokens to use.
